SDR enhancement by clouds

### 2024-02-26 article/article.Rmd
Commit 2024-02-26 13:11

---
title:    SDR enhancement by clouds
subtitle: A Short Subtitle
author:

  - name:  Athanasios N. Natsis
    email: natsisphysicist@gmail.com
    affiliations: 
        - id:          auth
          name:        Aristotle University of Thessaloniki
          department:  Laboratory of Atmospheric Physics
          address:     Campus Box 149 
          city:        Thessaloniki
          state:       Greece
          postal-code: 54124
    attributes:
        corresponding: true
    note: This is the first author footnote.
  - name:  Alkiviadis Bais
    email: abais@auth.gr
    affiliations:
        - id: another-u
          name: Another University
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
    note: |
      Another author footnote, this is a very long footnote and it should be a really long footnote. But this footnote is not yet sufficiently long enough to make two lines of footnote text.
  - name:  Charikleia Meleti
    email: meleti@auth.gr
    affiliations:
        - ref: auth
    note: Yet another author footnote.
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
date:          last-modified
bibliography:  [bibliography.bib]
format:
  elsevier-pdf:
    keep-tex:     true
    journal:
      name:       Journal Name
      formatting: preprint
      model:      3p
      cite-style: authoryear
  docx: default
  html: default
editor_options: 
  chunk_output_type: console
---

```{r setup, echo=F, include=T, warning=FALSE, message=FALSE}
suppressMessages(
    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
)
## document configurations
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
library(dplyr)
## load data from trends analysis
source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
load("~/MANUSCRIPTS/02_enhancement/data/GHI_enh_03_process.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
# ## create local citations file and links here
# source("~/CODE/FUNCTIONS/R/gather_citations.R")
# suppressMessages(
#     gather_citations(
#         sourcefile   = "./Article.Rmd",
#         mainreposit  = "./Mainreferences.bib",
#         localreposit = "./references.bib",
#         folderlink   = "./References_links",
#         workingdir   = "./"
#     )
# )
```

@@

@@

$$
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{if $\theta \leq `r C4_lowcut_sza`^\circ$}.\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{if $ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}.
\end{cases}
$${#eq-test}

-   some other were tested

@@

::: callout-important
## gcff

This is nice
:::

<!--# check this out -->

# Bibliography styles

Here are two sample references: @Feynman1963118 @Dirac1953888.

By default, natbib will be used with the `authoryear` style, set in `classoption` variable in YAML. You can sets extra options with `natbiboptions` variable in YAML header. Example

```         
natbiboptions: longnamesfirst,angle,semicolon
```

There are various more specific bibliography styles available at <https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files>. To use one of these, add it in the header using, for example, `biblio-style: model1-num-names`.

## Using CSL

If `cite-method` is set to `citeproc` in `elsevier_article()`, then pandoc is used for citations instead of `natbib`. In this case, the `csl` option is used to format the references. By default, this template will provide an appropriate style, but alternative `csl` files are available from <https://www.zotero.org/styles?q=elsevier>. These can be downloaded and stored locally, or the url can be used as in the example header.

@eq-lowbap

@@

# Equations

Here is an equation: $$ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
$$ {#eq-lowbap}

Inline equations work as well: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$

# Figures and tables

@fig-meaningless is generated using an R chunk.

```{r}
#| label: fig-meaningless
#| fig-cap: A meaningless scatterplot
#| fig-width: 5
#| fig-height: 5
#| fig-align: center
#| out-width: 50%
#| echo: false
plot(runif(25), runif(25))
```

# Tables coming from R

Tables can also be generated using R chunks, as shown in @tbl-simple example.

```{r}
#| label: tbl-simple
#| tbl-cap: Caption centered above table
#| echo: true
knitr::kable(head(mtcars)[,1:4])
```

>>>>

---
title:    SDR enhancement by clouds
subtitle: A Short Subtitle
author:
  - name:         Athanasios N. Natsis 
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
    footnote:     footnote one
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
  - name:         Charikleia Meleti
    email:        meleti@auth.gr
    affiliation:  Laboratory of Atmospheric Physics
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
date:          last-modified
bibliography:  [bibliography.bib]

output: 
 #  rticles::mdpi_article:
 #    extra_dependencies:  longtable
 #    keep_tex:            yes
  bookdown::word_document2: default
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
---

```{r setup, echo=F, include=T, warning=FALSE, message=FALSE}
suppressMessages(
    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
)
suppressMessages({
renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
})
## document configurations
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
library(dplyr)
## load data from trends analysis
source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
load("~/MANUSCRIPTS/02_enhancement/data/GHI_enh_03_process.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
# ## create local citations file and links here
# source("~/CODE/FUNCTIONS/R/gather_citations.R")
# suppressMessages(
#     gather_citations(
#         sourcefile   = "./Article.Rmd",
#         mainreposit  = "./Mainreferences.bib",
#         localreposit = "./references.bib",
#         folderlink   = "./References_links",
#         workingdir   = "./"
#     )
# )
```

@@

 \ref{eq:test}

@@

\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{if $\theta \leq `r C4_lowcut_sza`^\circ$}.\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{if $ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}.
\end{cases}\label{eq:test}
\end{equation}

```{r echo=FALSE, fig.cap="", out.width = '100%'}
knitr::include_graphics("../images/climCEmonth-1.png")
```

-   some others were tested

@@

## render test

@@
